Forecasting the 2024 U.S. Presidential Election: A Poll-of-Polls Approach for Predicting the Outcome

### 2024-11-04 paper/paper.qmd
fix data + add sketch

##Data visualization 
### Heatmap of Polling Percentage by State for Selected Pollsters
```{r}
#| warning: false
#| message: false
#| label: fig-heatmap
#| fig_caption: true
#| fig-cap: "Heatmap of Polling Percentage by State for Selected Pollsters across various states"
#| echo: false

>>>>

## Data visualization

### Heatmap of Polling Percentage by State for Selected Pollsters
```{r}
#| warning: false
#| message: false
#| label: fig-heatmap
#| fig_caption: true
#| fig-cap: "Heatmap of Polling Percentage by State for Selected Pollsters across various states"
#| echo: false
